\documentclass[10pt]{article}

\usepackage{ifthen}
\usepackage{geometry}
\usepackage[usenames,dvipsnames]{color}
\usepackage{marvosym}
\usepackage{wasysym}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{fontspec}
\usepackage{fontawesome}
\setmainfont[Ligatures=TeX]{Lato-Thin.ttf}

\thispagestyle{empty}\pagestyle{empty}

% No indent and increased paragraph spacing
\setlength{\parindent}{0pt}

% Configure margins:
\geometry{top=2.5cm,bottom=2.5cm,left=3.5cm,right=3.5cm}

% Commands
% - \cvtitle{Name}{ColorForName}{LiteralsOrRightText}{SpaceBelow} - Creates the CV title
\newcommand{\cvtitle}[4] {%
	{\LARGE\color{#2}\textsc{#1}}\hspace{\stretch{3}}{\large \textbf{#3}}\\[#4]}

% - \positionedbox{TextSide}{Width}{TextContent} - Creates a box of given width with text aligned as specified by 'TextSide' of given width. Note if you use box sizes which are less that the width of the page they can wrap together , ie 2 boxes of size 0.5\textwidth will sit side by side
\newcommand{\positionedbox}[3]{%
	\begin{minipage}{#2}
		\begin{flush#1}
			#3
		\end{flush#1}
	\end{minipage}}

% \cvskill{skill}{type}: Creates a 'skill' bullet. 'skill' is the actual skill text and 'type' is one of 'full', 'semi' or 'none' to indicate whether a full, half-full or empty bullet circle should be used.
\newcommand{\cvskill}[2]{\hspace{4mm}%
	\ifthenelse{\equal{#2}{full}}%
		{\CIRCLE~ }%
		%else%
		{\ifthenelse{\equal{#2}{semi}}%
			{\LEFTcircle ~ }%
			{\Circle ~ }}#1\\}

% \cvsectiontitle{title}: Creates a section with the given title.
\newcommand{\cvsectiontitle}[1]{%
	\rule{\linewidth}{0.2mm}\\%
		{\large\indent\textsc{#1}}\\%
	\\[-6mm]\rule{\linewidth}{0.2mm}\\[2mm]%
	}

% \cvpub{Authors}{Title}{Date}{Journal/Conference}{Pages}: Create a publication entry
\newcommand{\cvpub}[5]{#1. (#3) ``#2'' \emph{#4}, pages #5}

% \cvcompany{Name}{Date}: A new company in the experience section
\newcommand{\cvcompany}[2]{\textbf{#1}\hspace{\stretch{3}}{(#2)}}

% \cvsublevel{Text}: Create an indented item list
\newcommand{\cvsublevel}[1]{\begin{itemize}[leftmargin=0.5cm] #1\end{itemize}}

% \cvsubbullet{Text}: Create a buller in the sub level
\newcommand{\cvsubbullet}[1]{\vspace{-1mm}\item #1}

% Modify List enviroment
\renewcommand{\labelitemi}{\RIGHTarrow}
\renewcommand{\labelitemii}{$\bullet$}
\renewcommand{\labelitemiii}{\RIGHTarrow}
\renewcommand{\labelitemiv}{\RIGHTarrow}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                    Content                                       %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\cvtitle{Clement Hoang}{BrickRed}{}{0.5cm}
\positionedbox{left}{0.7\textwidth}{
	\begin{tabular}{ c l }
		{\FA \faMobile} & 647 871 8336 \\
		{\FA \faEnvelope} & c8hoang@uwaterloo.ca \\
		{\FA \faGithub} & https://github.com/clemmy
	\end{tabular}
}
\vspace{0.2cm}

\cvsectiontitle{Experience}
\vspace{-0.8cm} % NOTE: There are spacing issues, not sure why, fix them with some vspace
\begin{itemize}[leftmargin=0.5cm]
\item \cvcompany{Ten Thousand Coffees}{January 2015 - May 2015}\cvsublevel{
	\cvsubbullet{Improved user retention on platform and designer/developer workflow by using templating with Mandrill for transactional and digest emails with Segment.io for analytics tracking.}
	\cvsubbullet{Made email verification architecture stateless by switching manually generated bcrypt verification tokens to JWT.}
	\cvsubbullet{Redesigned the entire messaging system to support multiple participants and an user-friendly scheduling system that was pushed to production.}
	\cvsubbullet{Added internationalization support for the entire application with angular-translate.}
	}
\item \cvcompany{Objectifi}{April 2014 - August 2014}\cvsublevel{
	\cvsubbullet{Enhanced robustness of financial software used by major banking corporations worldwide by fixing database and UI defects.}
	\cvsubbullet{Wrote E2E regression tests with a web interface that allowed company employees to configure and run tests on different staging environments with real-time logs.}
	\cvsubbullet{Improved company workflow by over 30\% by automating daily tasks such server updates, builds, maintenance, and server monitoring}
	}
\end{itemize}

\cvsectiontitle{Projects} %http://clementhoang.net/\#work
\vspace{-0.8cm}
\begin{itemize}[leftmargin=0.5cm]
\item \cvcompany{Chidori}{April 2015 - now}\cvsublevel{
	\cvsubbullet{A cross platform Yugioh client where players can duel against one another online.}
	\cvsubbullet{Built with Electron, Sass, Bourbon, Neat, and MySQL}
}
\item \cvcompany{Hearthnet}{January 2015 - now}\cvsublevel{
	\cvsubbullet{A social platform for Hearthstone players to find other players with similar preferences.}
	\cvsubbullet{Built with Meteor, Sass, Bourbon, Neat, and MongoDB}
}
\item \cvcompany{BCQueue}{July 2013 - October 2013}\cvsublevel{
	\cvsubbullet{Feature-rich badminton club management software for Windows that features a members database, asynchronous court timers, and a queuing system.}
	\cvsubbullet{Built with WPF, C\#, .NET 4.0, XAML, Blend}
}
\end{itemize}

\cvsectiontitle{Skills}
\positionedbox{left}{0.6\textwidth}{
\cvskill{computer hacking skills}{full}
\cvskill{unchuku skills, bow hunting skills}{semi}
}
\positionedbox{left}{0.4\textwidth}{
\cvskill{bred for my skills in magic}{full}
\cvskill{NotAmazingAtThis...Yet}{none}
}
\\[0.4cm]
[\textbf{StuffIKnow}] \LaTeX, Tool, AnotherTool\\[0.2cm]
[\textbf{Natural Languages}] \emph{Native}: English, \emph{Passive}: LoLSpeak

% Personal information, hobbies etc
\cvsectiontitle{About Me}
Stuff n' Things.

\end{document}
